Staged Abstract Interpreters

### 2018-10-21 paper/10_intro.tex
refactor AC 0CFA

1. we know how to stage an interpreter, natural to ask how to stage an abstract interpreter, given 
the structural similarity of interpreters and abstract interpreters. Futamura projection \cite{Futamura1999}

2. precise whole-program analysis can be very slow, how to optimize it systematically/mechanically?
bridging the gap between designing sound analyses and implementing efficient analyses.

>>>>

1. we know how to stage an interpreter, intellectually it is natural to ask what would be an staged abstract interpreter,
and how to stage an abstract interpreter, given the structural similarity of interpreters and abstract interpreters. 
Futamura projection \cite{Futamura1999}

2. Multi-stage programming is widely used in high performance computation.
Precise whole-program analysis can be very slow, how to optimize it systematically/mechanically?
bridging the gap between designing sound analyses and implementing efficient analyses.

When staging a concrete interpreter, the programmers need to distinguish static and dynamic values
--- the given program is classified as static because it is known at compile-time, and the inputs to that program 
are dynamic. However, when staging an abstract interpreter, this distinction not exists anymore. 
Because an abstract interpreter treats all the inputs as some form of abstract values, which usually are 
top elements in their abstract domains and are statically known. Then what is the point of staging?
A surprising by-product of thinking about this question is to realize that we can apply the staged
abstract interpreter on \textit{open} programs, and the free variables representing other parts of 
the program (e.g., libraries) are dynamic input, then we obtain a modular analysis, mechanically.
